---
title: "Lab 00 - Hello IDS!"
author: "Mariam El Mardenly"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Mariam", "Kiki", "Fransesca", 
           "member 3", "member 4"),
  github_username = c("mariam0306", "kiki-xox", "username 2", 
                      "username 3", "username 4"), 
  colour = c("turquoise", "blue", "colour 2", 
             "colour 3", "colour 4"),
  hobby = c("reading", "football", "hobby 2", 
            "hobby 3", "hobby 4"),
  favourite_number = c(3, 4, NA, NA, NA)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


I see a bar chart where the x-axis shows the username of every member and a bar that rises up to their favourite number, as displayed on the y-axis.The colour of the bars of the bar chart are the favourite colour of the group member.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github username", 
          y = "Favourite number",
          title = "Favourite colour and number of team's github users")
```

The labs command allows you to change the labels of a graph or plot.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

This bar chart is a bad visualisation as it shows how many people do which hobby , not who does which hobby, and could only be more useful if more than one person does each hobby. Furthermore, if there were more hobbies, the graph would get far too wide and untidy. I would recommend a visualisation which allows the display of what each user's hobby is, rather than how many user's correspond to each hobby.
